Explicit B-spline regularization in diffeomorphic image registration

### 2013-10-28 paper.tex
ENH:  Walking dead.

\begin{figure}[htb]
  \centering
    \includegraphics[width=0.95\textwidth]{jacobianRange.jpg}
  \caption{Violin plots of the range of log Jacobian values 
           (95th\% - the 5th\%)  
           for all deformable
           transforms from each subject to its corresponding
           template.  B-spline SyN demonstrates a tendency 
           to produce a much
           greater range of log Jacobian values.
           }
  \label{fig:jacobian}
\end{figure}

>>>>

\begin{figure}[htb]
  \centering
    \includegraphics[width=0.95\textwidth]{jacobianRange.jpg}
  \caption{Violin plots of the range of log Jacobian values 
           (95th\% - 5th\%)  
           for all deformable
           transforms from each subject to its corresponding
           template.  B-spline SyN demonstrates a tendency 
           to produce a much
           greater range of log Jacobian values.
           }
  \label{fig:jacobian}
\end{figure}
